### 2017-10-20 paper/sections/6_results.tex
paper: add some figs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\subsection{Microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-mechanisms.png}
\caption{
[\href{https://...}{source}]
The performance of the Cudele mechanisms normalized to the runtime of the
``Append Client Journal" mechanism (the runtime of writing \(n\) file creates
to the client's in-memory journal).  \label{fig:slowdown-mechanisms}}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/behavior-journal-size.png}
\caption{
[\href{https://...}{source}]
The size of the client's journal scales with the number of
updates.\label{fig:behavior-journal-size}}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/merge-a.png}
\caption{ [\href{https://...}{source}] Merging journals serially.}
\label{fig:merge}
\end{figure}

%\begin{figure}[t]
%  \centering
%  \begin{subfigure}[b]{\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{graphs/merge-a.png}
%      \caption{Merging journals serially.} \label{fig:merge-a}
%  \end{subfigure}\\
%  ~
%  \begin{subfigure}[b]{\linewidth}
%      \centering
%      \includegraphics[width=1.0\linewidth]{graphs/merge-b.png}
%      \caption{Merging a journal w/ 100K create updates.}
%      \label{fig:merge-b}
%  \end{subfigure}
%  \caption{Merging updates has linear scalability.\label{fig:merge}}
%\end{figure}

{\it Number of Serialized Merges:} Cudele serializes merge requests at the
metadata server before applying the updates to the in-memory metadata store.
Merging concurrently is an optimization for future work, but merges for the
largest journal size we tested were quite fast.  Furthermore, since we place no
restrictions on the validity of metadata inserted into the journal, we can
avoid touching poorly scaling data structures. In other words, we can scale
linearly if we weaken our consistency by never checking for the existence of
files before creating files.

Figure~\ref{fig:merge} demonstrates this scalability by showing the runtime
(\(y\) axis) of merging journals of different sizes (\(x\) axis). The variance
of the runtime is over 20 serial merges, each hitting a different directory in
the namespace.  The runtime scales linearly and with low variance because the
``Create" mechanism that was used to create the journal only appends
\texttt{open()} requests to the journal. When the updates are merged by the
metadata server into the in-memory metadata store they never scan growing data
structures. Had we implemented the ``Create" mechanism to include
\texttt{lookup()} commands before \texttt{open()} requests, we would have seen
the poor scaling that we see with the ``RPCs" mechanism.\\
%Figure~\ref{fig:merge-b} confirms that we do not touch a poorly scaling data
%structure because the runtimes do not increase as we add more metadata. \\

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-strong-v-weak.png}
\caption{
[\href{https://...}{source}]
The RPC per metadata update of ``Strong Consistency" has a large
overhead compared to the decoupled namespace strategy of ``Weak
Consistency".\label{fig:slowdown-strong-weak}}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-allow-block.png}
\caption{
[\href{https://...}{source}]
Using the ``allow" and ``block" API, users can isolate directories from
interfering clients. Variance with blocking turned on is the same as
``isolated" from Figure~\ref{fig:overhead-b}.
\label{fig:slowdown-allow-block}}
\end{figure}

@@

\begin{figure}[tb] \centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png} \caption{
[\href{https://...}{source}] Slowdown of a single client periodically syncing
updates to the gobal namespace. The crossover point represents the trade-off of
frequent updates (with small journal files) and infrequent updates (with larger journal
files).\ref{fig:slowdown-sync}.  \label{fig:slowdown-sync}} \end{figure}

@@

To show the contention at the metadata server of this approach, we scale the
number of concurrent journal merge events in FigureX. The size of each journal
is 100K files, the maximum recommended directory size for CephFS. We also plot
the cost of RPCs with and without journaling.

>>>>

\subsection{Microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-mechanisms.png}
\caption{ [\href{https://...}{source}] Microbenchmark: performance of each
mechanism. Results are normalized to the runtime of the ``Append Client
Journal" mechanism (the runtime of writing \(n\) file creates to the client's
in-memory journal).  \label{fig:slowdown-mechanisms}}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/behavior-journal-size.png}
\caption{ [\href{https://...}{source}] Microbenchmark: storage footprint on
client. The size of the client's journal scales with the number of
updates.\label{fig:behavior-journal-size}}
\end{figure}

@@

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-strong-v-weak.png}
\caption{ [\href{https://...}{source}] Use Case 1: the RPC per metadata update
(strong consistency) has a large overhead compared to decoupled namespaces
(weak consistency.)\label{fig:slowdown-strong-weak}}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-allow-block.png}
\caption{ [\href{https://...}{source}] Use Case 2: using the ``allow" and
``block" API, users can isolate directories from interfering clients. Variance
with blocking turned on is the same as ``isolated" from
Figure~\ref{fig:overhead-b}.
\label{fig:slowdown-allow-block}}

\end{figure}

@@

\begin{figure}[tb] \centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png} \caption{
[\href{https://...}{source}] Use Case 3: slowdown of a single client periodically syncing
updates to the gobal namespace. The crossover point represents the trade-off of
frequent updates (with small journal files) and infrequent updates (with larger journal
files).\ref{fig:slowdown-sync}.  \label{fig:slowdown-sync}} \end{figure}

@@

To show the contention at the metadata server of this approach, we scale the
number of journal merge events, each hitting different directories
in the namespace, in FigureX. The size of each journal is 100K files, the
maximum recommended directory size for CephFS. We also plot the cost of RPCs
with and without journaling.

Merge requests are serialized at the metadata server; merging concurrently is
an optimization for future work. The current implementation has race conditions
because the metadata server recovery code was not designed to run in parallel
({\it i.e.} the metadata server never recovers with multiple threads). As a
result, the metadata server versions inodes and directory entries to ensure
that the recovered metadata is consistent.

Performance is better than RPCs because we place no restrictions on the
validity of metadata inserted into the journal and avoid touching poorly
scaling data structures. In other words, we can scale linearly if we weaken our
consistency by never checking for the existence of files before creating files.
only appends \texttt{open()} requests to the journal. When the updates are
merged by the metadata server into the in-memory metadata store they never scan
growing data structures.  Had we implemented the ``Create" mechanism to include
\texttt{lookup()} commands before \texttt{open()} requests, we would have seen
the poor scaling that we see with the ``RPCs" mechanism.\\
